---
title: "Data Visualization"
author: "Aditi Arunmozhi"
date: "7/21/2022"
output: html_document
---

```{r setup}
library(tidyverse)
library(glamr)
library(gophr)
library(scales)
library(gridExtra)
library(grid)
library(glitr)
library(ggplot2)
library(stats)
library(ggrepel)
library(scales)
library(tidyverse)
library(janitor)

# #msd <- read_delim("MER_Structured_Datasets_PSNU_IM_FY20-23_20220617_v2_1.zip", delim = "\t", escape_double = FALSE, trim_ws = TRUE, 
#               col_types = cols(.default = "c",
#                           targets	= "d",
#                           qtr1	= "d",
#                           qtr2	= "d",
#                           qtr3	= "d",
#                           qtr4	= "d",
#                           cumulative = "d"))
```


Transform

```{r}
indicator_list <- c("KP_PREV",  "HTS_SELF", "HTS_TST", "HTS_TST_NEG", "PrEP_NEW", "PrEP_CT", "PrEP_CURR", "HTS_TST_POS",
                    "TX_NEW", "TX_CURR", "TX_PVLS", "TX_PVLS_D", "TX_PVLS_N", "TX_CURR_Lag1", "TX_CURR_Lag2", "TX_ML", "TX_NET_NEW")

 df <- df %>% filter(fiscal_year >= 2021, #cumulative and targets
                    fiscal_year < 2023,
                    str_detect(standardizeddisaggregate, "KeyPop|Total") == TRUE,
                    indicator %in% indicator_list)
 MER <- df %>% mutate(indicator = factor(indicator, levels = indicator_list)) %>% arrange(indicator) %>% glimpse()
df

check <- df %>% filter(disaggregate != "KeyPop/Status") %>%
  mutate(cumulative = coalesce(cumulative, 0),
         targets = coalesce(targets, 0),
         fy = fiscal_year,
         partner = prime_partner_name,
         disagg = str_extract(standardizeddisaggregate, "Total|KeyPop"),
         disagg = recode(disagg, "KeyPop" = "KP"),
         tx_ml_reason = case_when(indicator=="TX_ML" ~ str_extract(otherdisaggregate, "(?<=Outcome\\s-\\s).+")),
         keypop = str_extract(otherdisaggregate, "FSW|MSM|TG|PWID|People\\sin\\sprisons"),
         keypop = recode(keypop, "People in prisons" = "Prisoners"),
         indicator = recode(indicator, "TX_PVLS" = paste0(indicator,"_", numeratordenom))) %>%
  select(operatingunit, country, snu1, psnu, partner, mech_code, mech_name, indicator, funding_agency, numeratordenom, disagg, disaggregate, tx_ml_reason, keypop, fy, targets, cumulative) %>%
  mutate(indicator = factor(indicator, levels = indicator_list)) %>% arrange(indicator) %>%
  glimpse()


qcheck <- df %>% filter(fiscal_year >= 2021, #cumulative and targets
                       str_detect(standardizeddisaggregate, "KeyPop|Total") == TRUE,
                       disaggregate != "KeyPop/Status") %>%
  mutate(cumulative = coalesce(cumulative, 0),
         targets = coalesce(targets, 0),
         fy = fiscal_year,
         partner = prime_partner_name,
         disagg = str_extract(standardizeddisaggregate, "Total|KeyPop"),
         disagg = recode(disagg, "KeyPop" = "KP"),
         keypop = str_extract(otherdisaggregate, "FSW|MSM|TG|PWID|People\\sin\\sprisons"),
         keypop = recode(keypop, "People in prisons" = "Prisoners"),
         indicator = recode(indicator, "TX_PVLS" = paste0(indicator,"_", numeratordenom))) %>%
  select(operatingunit, country, snu1, psnu, partner, mech_code, mech_name, indicator, funding_agency, numeratordenom, disagg, disaggregate, keypop, fy, qtr1, qtr2, qtr3, qtr4) %>%
  pivot_longer(qtr1:qtr4, names_to = "qtr", values_to = "results" ) %>%
  mutate(qtr = str_replace(qtr, "qtr","Q"),
         fyq = paste0("FY",str_extract(fy, "..$"), " ", qtr)) %>%
  mutate(indicator = factor(indicator, levels = indicator_list)) %>% arrange(indicator) %>%
  glimpse()

```

1. Positive or Prevention Cascade - 1 country - choose other filters, FY or quarter view

```{r}
pos <-  c("HTS_TST_POS", "TX_NEW", "TX_CURR", "TX_PVLS_D", "TX_PVLS_N")
neg <-  c("KP_PREV", "HTS_TST", "HTS_TST_NEG", "HTS_SELF", "PrEP_NEW", "PrEP_CT", "PrEP_CURR")

#negative cascade
cascade <- check %>% filter(fy == "2021", disagg == "KP", country == "Botswana",
                            indicator %in% neg, str_detect(mech_name, "EpiC")) %>%
  group_by(fy, indicator) %>%
  summarise(sum.cum=sum(cumulative), sum.targets=sum(targets)) %>%  
  mutate(ach = sum.cum/sum.targets) %>%
  ggplot2::ggplot(aes(x = indicator, y = sum.cum, fill = factor(fy)))

cascade + geom_col(aes(y = sum.targets, fill= "Target")) + geom_col(aes(y=sum.cum, fill= "Cumulative"), width = 0.75) + geom_label(position = position_stack(vjust = 0.9), aes(label = percent(ach, accuracy = 0.1))) + scale_fill_discrete(labels = c("Achievement", "Cumulative", "Target"))+ si_style()
```
2. TX_PVLS (D) an (N) bar chart by quarter - 1 country - choose other filters, labels 

```{r}
tx_pvls_indicators <- c("TX_PVLS_N", "TX_PVLS_D")

measure_trends_tx_pvls_bots <- qcheck %>% filter(country == "Botswana", disagg == "KP", results!=0, indicator %in% tx_pvls_indicators) %>%
  group_by(fyq, country, indicator) %>%
  summarise(sum.results=sum(results))

ggplot(measure_trends_tx_pvls_bots, aes(x = fyq, y = sum.results, group=indicator)) + geom_col(aes(fill = indicator), position = position_dodge()) + si_style()

#vlc with tx_pvls_d
#vls with tx_pvls_n
```

3. Scatter plot of VLC and VLS, each shape is a PSNU - 1 country, FY22 cumulative - choose other filters, labels (New)
group by statement to feature snu, psnu, Scatter plot 5b


```{r}
measure_indicators <- c("TX_PVLS_N", "TX_PVLS_D", "TX_CURR_Lag1", "TX_CURR_Lag2", "HTS_TST_POS", "TX_NEW", "HTS_TST_NEG", "PrEP_NEW")
fy22 <- c("FY22 Q1","FY22 Q2")

measure_trends_bots <- check %>% filter(country == "Botswana", disagg == "KP", cumulative!=0, indicator %in% measure_indicators, fy == 2022) %>%
  group_by(fy, country, indicator, psnu) %>%
  summarise(sum.cumulative=sum(cumulative)) %>%
  pivot_wider(values_from = sum.cumulative, names_from = indicator) %>%
  mutate(vls = TX_PVLS_N/TX_PVLS_D,
         vlc = TX_PVLS_D/TX_CURR_Lag2,
         linkage = TX_NEW/HTS_TST_POS) %>% na.omit()

measure_trends_bots %>% ggplot2::ggplot(aes(x = vlc, y = vls, label = psnu)) + geom_text(size = 2.5, vjust = 0, nudge_y = 0.025) + xlim(.4,1.1) + ylim(.4, 1.1) + geom_point(size = 4) + si_style()
```

4. Scatter plot of HTS_TST_POS and TX_NEW  label marks with Key Population and "Proxy Linkage" calculation (TX_NEW/HTS_TST_POS) - 1 country, FY22 cumulative - choose other filters, labels (New)

```{r}
linkage_zim <- check %>% filter(country == "Zimbabwe", disagg == "KP", cumulative!=0, indicator %in% measure_indicators, fy == 2022) %>%
  group_by(fy, country, indicator, keypop) %>%
  summarise(sum.cumulative=sum(cumulative)) %>%
  pivot_wider(values_from = sum.cumulative, names_from = indicator) %>%
  mutate(vls = TX_PVLS_N/TX_PVLS_D,
         vlc = TX_PVLS_D/TX_CURR_Lag2,
         linkage = TX_NEW/HTS_TST_POS) %>% na.omit()

linkage_zim %>% ggplot2::ggplot(aes(x = keypop, y = linkage)) + geom_point(size = 4) + si_style()
```

5. Comet chart of #4 (future)

```{r}
library(ggforce)
linkage_comet <- check %>% filter(country == "India", disagg == "KP", cumulative!=0, indicator == "HTS_TST_POS", fy == c(2021,2022)) %>%
  group_by(fy, country, keypop) %>%
  summarise(sum.cumulative=sum(cumulative)) %>%
  pivot_wider(values_from = sum.cumulative, names_from = fy)%>% clean_names() %>% glimpse()

#using previous quarter as starting point
linkage_comet %>% ggplot() + geom_link(aes(x = x2021, y = keypop, xend = x2022, yend = keypop, size = stat(index))) +
  scale_color_manual(values = c("#00A087FF", "#E64B35FF")) +
  geom_point(
    aes(x = x2021, y = keypop),
    shape = 21,
    fill = "white",
    size = 3.5
  )  +
  geom_point(
    aes(x = x2022, y = keypop),
    shape = 21,
    fill = "white",
    size = 3.5
  ) + si_style() + si_legend_color()
```
