---
title: "7ab"
format: html
editor: visual
---

```{r}
country3 <- "Ethiopia"
country4 <- "Vietnam"
country5 <- "Uganda"

```

## 2de 

2d HTS [Index, SNS: PEPFAR in country3](https://tableau.usaid.gov/views/KeyPopulationsDashboard/2_dPositivityTrends/80ee2627-5bd1-4aa3-842c-f07bc27c8baa/35dfff48-aeec-40c8-aa03-d4c58c7c0c00?:display_count=n&:showVizHome=n&:origin=viz_share_link) + [2e](https://tableau.usaid.gov/views/KeyPopulationsDashboard/2_ePositivityHTSVolTrendContributiuon/539d7ba9-25ca-4002-8508-c8abe9517b7f/0844c1d6-242a-499f-ae2c-0abdde58ada7?:display_count=n&:showVizHome=n&:origin=viz_share_link)

2de HTS [by agency, country 4](https://tableau.usaid.gov/views/KeyPopulationsDashboard/2_dPositivityTrends/9d44b010-ebe5-4a60-99c9-36391ac5106c/a0e88fdf-faac-4bd6-b42d-2c645c28016c?:display_count=n&:showVizHome=n&:origin=viz_share_link)

2de HTS [by KeyPop in country5](https://tableau.usaid.gov/views/KeyPopulationsDashboard/2_dPositivityTrends/33d4c902-23c5-4d98-b84f-9d256f0740a4/2780431a-34fc-460b-8257-6cbf6668b962?:display_count=n&:showVizHome=n&:origin=viz_share_link)

country3 \<- "Ethiopia"

country4 \<- "Vietnam"

country5 \<- "Uganda"

```{r}

modality %>%
  filter(country== country3,indicator %in% c("HTS_TST_POS", "HTS_TST"),
         str_detect(modality,"Index|SNS")) %>%
  select(country, indicator, modality, fyq, results) %>%
  group_by(country, indicator, modality, fyq) %>% 
  summarise(results = sum(results), .groups = 'drop') %>%
  pivot_wider(names_from = indicator, values_from = results) %>%
  mutate(positivity = percent(HTS_TST_POS/HTS_TST, accuracy = 1)) %>%
  print()

qcheck %>%
  filter(indicator %in% c("HTS_TST_POS", "HTS_TST"),
        country== country4,
        disagg == "KP") %>%
  select(country, indicator, funding_agency, fyq, results) %>%
  group_by(country, indicator, funding_agency, fyq) %>% 
  summarise(results = sum(results), .groups = 'drop') %>%
  pivot_wider(names_from = indicator, values_from = results) %>%
  mutate(positivity = percent(HTS_TST_POS/HTS_TST, accuracy = 1)) %>%
  print()

qcheck %>%
  filter(indicator %in% c("HTS_TST_POS", "HTS_TST"),
        country== country5) %>%
  select(country, indicator, keypop, fyq, results) %>%
  group_by(country, indicator, keypop, fyq) %>% 
  summarise(results = sum(results), .groups = 'drop') %>%
  pivot_wider(names_from = indicator, values_from = results) %>%
  mutate(positivity = percent(HTS_TST_POS/HTS_TST, accuracy = 1)) %>%
  print()
```

4a-c

4abc [country 4 by modality](https://tableau.usaid.gov/views/KeyPopulationsDashboard/4_bPositivityBarChartComparisons/4ae86c0e-d420-4931-a552-fd225911a4af/7d584d07-6605-4dce-8a5c-584d04ead6a3?:display_count=n&:showVizHome=n&:origin=viz_share_link)

4bc [country 5 by agency](https://tableau.usaid.gov/views/KeyPopulationsDashboard/4_bPositivityBarChartComparisons/f0920949-09d0-4894-abfd-4ae9869abca5/0271bbcf-2a30-434b-8491-30044e1ddd40?:display_count=n&:showVizHome=n&:origin=viz_share_link)

4abc [country3 by KP](https://tableau.usaid.gov/views/KeyPopulationsDashboard/4_bPositivityBarChartComparisons/fdbcacac-48f4-4771-a72f-77d299de0f97/04b66836-3e1c-4110-86e5-d85d95776fc6?:display_count=n&:showVizHome=n&:origin=viz_share_link)

4bc [country4 by SNU](https://tableau.usaid.gov/views/KeyPopulationsDashboard/4_bPositivityBarChartComparisons/a0fdd21b-8022-4810-801e-0045f9bdb448/5351f49d-d270-4142-92a5-15bdc349c2cf?:display_count=n&:showVizHome=n&:origin=viz_share_link)

4bc [country5 by PSNU](https://tableau.usaid.gov/views/KeyPopulationsDashboard/4_cPositivityScatterPlotComparisons/9195e614-e628-4685-81fa-89ecc4996bd2/dd047c24-bdff-405f-94a2-aaf23551b9fd?:display_count=n&:showVizHome=n&:origin=viz_share_link)

```{r}
#| echo: false

modality %>%
  filter(country== country4,
         fyq == current_fyq,
         indicator %in% c("HTS_TST_POS", "HTS_TST"),
     ) %>%
  select(country, indicator, modality, results) %>%
  group_by(country, indicator, modality) %>% 
  summarise(results = sum(results), .groups="drop") %>%
  pivot_wider(names_from = indicator, values_from = results) %>%
  mutate(positivity = percent(HTS_TST_POS/HTS_TST, accuracy = 1),
         positivity_frac = HTS_TST_POS/HTS_TST) %>%
  arrange(desc(positivity_frac)) %>% select(-positivity_frac) %>%
  print()

qcheck %>%
  filter(indicator %in% c("HTS_TST_POS", "HTS_TST"),
        country== country5,
        fyq == current_fyq,       
        disagg == "KP") %>%
  select(country, indicator, funding_agency, results) %>%
  group_by(country, indicator, funding_agency) %>% 
  summarise(results = sum(results), .groups="drop") %>%
  pivot_wider(names_from = indicator, values_from = results) %>%
  mutate(positivity = percent(HTS_TST_POS/HTS_TST, accuracy = 1),
         positivity_frac = HTS_TST_POS/HTS_TST) %>%
  arrange(desc(positivity_frac)) %>% select(-positivity_frac) %>%
  print()

qcheck %>%
  filter(indicator %in% c("HTS_TST_POS", "HTS_TST"),
        country== country3,
        fyq == current_fyq       
     ) %>%
  select(country, indicator, keypop, results) %>%
  group_by(country, indicator, keypop) %>% 
  summarise(results = sum(results), .groups="drop") %>%
  pivot_wider(names_from = indicator, values_from = results) %>%
  mutate(positivity = percent(HTS_TST_POS/HTS_TST, accuracy = 1),
         positivity_frac = HTS_TST_POS/HTS_TST) %>%
  arrange(desc(positivity_frac)) %>% select(-positivity_frac) %>%
  print()

qcheck %>%
  filter(indicator %in% c("HTS_TST_POS", "HTS_TST"),
        country== country4,
        fyq == current_fyq,       
        disagg == "KP") %>%
  select(country, indicator, snu1, results) %>%
  group_by(country, indicator, snu1) %>% 
  summarise(results = sum(results), .groups="drop") %>%
  pivot_wider(names_from = indicator, values_from = results) %>%
  mutate(positivity = percent(HTS_TST_POS/HTS_TST, accuracy = 1),
         positivity_frac = HTS_TST_POS/HTS_TST) %>%
  arrange(desc(positivity_frac)) %>% select(-positivity_frac) %>%
  print()

qcheck %>%
  filter(indicator %in% c("HTS_TST_POS", "HTS_TST"),
        country== country5,
        fyq == current_fyq,       
        disagg == "KP") %>%
  select(country, indicator, psnu, results) %>%
  group_by(country, indicator, psnu) %>% 
  summarise(results = sum(results), .groups = "drop") %>%
  pivot_wider(names_from = indicator, values_from = results) %>%
  mutate(positivity = percent(HTS_TST_POS/HTS_TST, accuracy = 1),
         positivity_frac = HTS_TST_POS/HTS_TST) %>%
  arrange(desc(positivity_frac)) %>% select(-positivity_frac) %>%
  print()
```
