---
title: "Older KP Analysis"
author: "Bourke Betz"
date: "2024-04-16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

```{r, include=FALSE}
library(tidyverse)
library(gagglr)
library(googlesheets4)

load_secrets()
```

Data were downloaded and read from PEPFAR panorama
```{r, include=FALSE}
ou_file_path <- glamr::return_latest(folderpath =  "../Data/", pattern = "OU_IM_FY2") |> print()
ou_file_name <- str_extract(ou_file_path, "(?<=Data\\/).+")  |> print()
ou_msd <- gophr::read_psd(file = ou_file_path)
```
```{r, include=FALSE}
#Define age groups for analysis
fiftyplus <- c("50+", "50-54", "55-59", "60-64", "65+")
fourtyplus  <- c("40-44", "45-49", "50+", "50-54", "55-59", "60-64", "65+")
fourties  <- c("40-44")
# fourties  <- c("40-44", "45-49")

```

```{r, echo=FALSE, warning=FALSE}
# read in EpiC IMs from 2 lists
epic_input <- read_sheet("https://docs.google.com/spreadsheets/d/1G3K5rXeU54FN54FehPa6LCsJLnAx0rD5aVtrJ5ys-hw/edit#gid=797015621",
                         sheet = 3) |> select(mech_code) |> mutate(mech_type = "Central KP Partner Mechanism") 

epic_input_old <- read_sheet("https://docs.google.com/spreadsheets/d/1G3K5rXeU54FN54FehPa6LCsJLnAx0rD5aVtrJ5ys-hw/edit#gid=797015621",
                         sheet = 5) |> filter(type=="Central KP Partner Mechanism") |> select(mech_code) |> 
                  mutate(mech_type = "Central KP Mechanism")

central_kp_mech_ims <- epic_input |> rbind(epic_input_old) |> count(mech_code, mech_type) |> select(-n)
```



Data were manipulated and transformed for analysis using R
```{r data_prep, include=FALSE}
plhiv_by_age <- ou_msd |>
  filter(indicator=="TX_CURR", !is.na(ageasentered), !standardizeddisaggregate == "Age/Sex/ARVDispense/HIVStatus") |> 
  mutate(mech_code = as.double(mech_code)) |> 
  # left_join(epic_ims, by = "mech_code") |> 
  mutate(age50plus = case_when(ageasentered %in% fiftyplus ~ "50+",
                               .default = "not 50+"),
         age40plus = case_when(ageasentered %in% fourtyplus ~ "40+",
                               .default = "not 40+"),
         age40s = case_when(ageasentered %in% fourties ~ "40s",
                               .default = "not 40s"),
         ) |> 
  group_by(funding_agency, mech_code, age50plus, age40plus, age40s, fiscal_year, indicator) |> 
  summarise(values=sum(cumulative, na.rm = TRUE), .groups = "drop")

```

#create functions
```{r functions,  include=FALSE}

filter_scope <- function(df, funding_agency_selection = NULL, mech_type = NULL) {
      if (!is.null(funding_agency_selection)) {
      df2 <-  df |> filter(funding_agency == {{funding_agency_selection}})
      }
      else if (!is.null(mech_type)) {
      df2 <-    df |> 
            inner_join({{mech_type}}, by = "mech_code")
        }
      else {
        df2 <- df
      }
  return(df2)
}

test1 <- plhiv_by_age |> filter_scope(mech_type = central_kp_mech_ims)
test1 |> count(funding_agency)


sum_values_by_agecat <- function (df, agecat) {
      df3 <- df |>   
      group_by({{agecat}}, fiscal_year) |> 
      summarise(values=sum(values, na.rm = TRUE), .groups = "drop") |> 
      rename_with(~ "age", 1) |> 
      group_by(fiscal_year) |> 
      mutate(total=sum(values, na.rm = TRUE),
             proportion = scales::percent(values/total)) |> ungroup() |> 
      filter(!str_detect(age, "^not"))
  #   }    
  return(df3)
}


#test
test2 <- plhiv_by_age |> 
  sum_values_by_agecat(agecat = age50plus) |> print()


#iterate
# agecolumns <- c("age50plus", "age40plus", "age40s")

#CANNOT ITERATE
# result_df <- map_df(agecolumns, ~ sum_values_by_agecat(plhiv_by_age, agecat = .x))

```


New enhanced function with 3 parts, to be used after filter_scope()
```{r functions_plus,  include=FALSE}

sum_values_by_agecat_plus <- function (df, agecat, keep_funding_agency = NULL, keep_mech_type = NULL) {
    if (keep_funding_agency == TRUE & is.null(keep_mech_type)) {
      df3 <- df |>
      group_by({{agecat}}, fiscal_year, funding_agency) |>
      summarise(values=sum(values, na.rm = TRUE), .groups = "drop") |>
      rename_with(~ "age", 1) |>
      group_by(fiscal_year) |>
      mutate(total=sum(values, na.rm = TRUE),
             proportion = scales::percent(values/total)) |> ungroup() |>
      filter(!str_detect(age, "^not"))
         }
    else if (keep_mech_type == TRUE & is.null(keep_funding_agency)) {
      df3 <- df |>
      group_by({{agecat}}, fiscal_year, mech_type, funding_agency) |>
      summarise(values=sum(values, na.rm = TRUE), .groups = "drop") |>
      rename_with(~ "age", 1) |>
      group_by(fiscal_year) |>
      mutate(total=sum(values, na.rm = TRUE),
             proportion = scales::percent(values/total)) |> ungroup() |>
      filter(!str_detect(age, "^not"))
        }
    else if (keep_funding_agency == TRUE & keep_mech_type == TRUE) {
      df3 <- df |>
      group_by({{agecat}}, fiscal_year, mech_type, funding_agency) |>
      summarise(values=sum(values, na.rm = TRUE), .groups = "drop") |>
      rename_with(~ "age", 1) |>
      group_by(fiscal_year) |>
      mutate(total=sum(values, na.rm = TRUE),
             proportion = scales::percent(values/total)) |> ungroup() |>
      filter(!str_detect(age, "^not"))
         }
    else if (is.null(keep_funding_agency) & is.null(keep_mech_type)) {
      df3 <- df |>
      group_by({{agecat}}, fiscal_year) |>
      summarise(values=sum(values, na.rm = TRUE), .groups = "drop") |>
      rename_with(~ "age", 1) |>
      group_by(fiscal_year) |>
      mutate(total=sum(values, na.rm = TRUE),
             proportion = scales::percent(values/total)) |> ungroup() |>
      filter(!str_detect(age, "^not"))
    }
      else {stop("m")}
  
  return(df3)

}

test5 <- plhiv_by_age |> 
  filter_scope(mech_type = central_kp_mech_ims) |>
  sum_values_by_agecat_plus(agecat = age50plus,  keep_funding_agency = TRUE, keep_mech_type = TRUE) |> print()



```
# HOW to add warnings and notes, use the function cat
example  cat("No columns found where all values are the same across all rows. Default name 'output' used.\n")


# approach worked but these approaches were too complicated, settled on an approach which simplified the actions into one command because the sum_values_by_agecat_plus was dependent on filter_scope
