---
title: "People in prisons targets"
author: "Bourke Betz"
format: html
editor: visual
execute: 
  fig-width: 8
  fig-asp: 0.618
  fig-align: center
  warning: FALSE
  message: FALSE
---

## Identify a list of OUs and indicators with targets for People in prisons

### list packages

```{r}
#| echo: false

library(tidyverse)
library(janitor)
library(gagglr)
library(patchwork)


```

## transform

Started with OU-level data, filtered to the last 2 fiscal years, people in prisons, and targets \>0

```{r}
#| echo: false
rds <- glamr::return_latest(folderpath =  "../../Data/", 
                            pattern = "OU_IM_FY2.+\\.rds")
```

```{r}
#| echo: false
prisoner_targets <- readRDS(file = rds) |>
  filter(fiscal_year >= max(fiscal_year)-2,
         !indicator %in% c("HTS_RECENT", "PrEP_CURR"),
         disaggregate != "KeyPop/Status",
         otherdisaggregate_sub == "People in prisons and other enclosed settings")
```

## group by indicator, ou to showcase trends

```{r}
annual_cols <- c("targets", "cumulative")
indicators_with_denominators <- prisoner_targets |> filter(numeratordenom=="D") |> group_by(indicator) |> summarise() |> as.list()


usaid_pip <- prisoner_targets |>   
  filter(funding_agency == "USAID") |> 
  mutate(pop = tolower(otherdisaggregate_sub),
         indicator = if_else(indicator %in% indicators_with_denominators, 
         str_c(indicator, numeratordenom, sep="_"), 
         indicator),
         country = if_else(country=="Democratic Republic of the Congo", 
                           "DRC", country)) |> 
  group_by(operatingunit, country, indicator, numeratordenom, 
           pop, funding_agency, fiscal_year) |> 
  summarise(across(all_of(annual_cols), ~sum(.x, na.rm = TRUE)),  .groups = "drop") 



pepfar_pip <- prisoner_targets |>      
  mutate(pop = tolower(otherdisaggregate_sub),
         indicator = if_else(indicator %in% indicators_with_denominators, 
         str_c(indicator, numeratordenom, sep="_"), 
         indicator),
         country = if_else(country=="Democratic Republic of the Congo", 
                           "DRC", country)) |> 
  group_by(operatingunit, country, funding_agency, indicator, numeratordenom, 
           pop, fiscal_year) |> 
  summarise(across(all_of(annual_cols), ~sum(.x, na.rm = TRUE)),  .groups = "drop")


```

name cascade order

```{r}
ind_prev <- c("KP_PREV", "HTS_SELF", "HTS_TST", "HTS_TST_NEG", "PrEP_NEW")
ind_tx <- c("HTS_TST_POS", "TX_NEW", "TX_CURR", "TX_PVLS_D", "TX_PVLS_N")
```

## Check snapshot TX cascade totals and achievment

only discrepancy was the casefinding and TX_NEW as some clients who are referred are excluded to facillitate use of custom indicators. Numbers match cascades, but intentionally do not match the high level numbers pos and tx_new numbers which reflect deduplication.

```{r}
# top <- 
p_ut <- usaid_pip |> filter(indicator %in% ind_tx) |>  
  group_by(fiscal_year, indicator, funding_agency, pop) |> 
  summarise(across(targets:cumulative, ~sum(.x, na.rm = TRUE)), .groups = "drop") |> 
  mutate(indicator = fct_relevel(indicator, ind_tx),
         top_col = if_else(cumulative >= targets, cumulative, targets),
         target_ach = case_when(!(is.na(targets) | targets==0) ~ 
                                  cumulative/targets)) |> 
    arrange(desc(fiscal_year), desc(funding_agency)) |> print()

  
p_ut |> ggplot(aes(x=indicator)) +
  geom_col(aes(y=targets), fill=grey20k) +
  geom_col(aes(y=cumulative), width =0.5, fill=scooter) +
  geom_text(aes(y=top_col,
                label = scales::percent(target_ach, accuracy=1)),
            vjust=-0.75, size=5, color=grey80k) +
  facet_wrap(~fiscal_year, nrow = 1) +
  si_style_xyline() +
  # ylim(0,2300) +
  theme(plot.title = element_text(size = 18),
        axis.title = element_blank(),
        axis.text.x = element_text(angle = 90, hjust = 1, size=14),
        strip.text = element_text(face="bold", size=18, hjust=0.5)) +
  labs(title = str_glue("FY23Q2 {p_ut$funding_agency} treatment cascade trehds for {p_ut$pop}"),
       subtitle = "")

```

## Check snapshot prevention cascade totals and achievment,

no issues

```{r}
# top <- 
p_up <- usaid_pip |> filter(indicator %in% ind_prev) |>  
  group_by(fiscal_year, indicator, funding_agency, pop) |> 
  summarise(across(targets:cumulative, ~sum(.x, na.rm = TRUE)), .groups = "drop") |> 
  mutate(indicator = fct_relevel(indicator, ind_prev),
         top_col = if_else(cumulative >= targets, cumulative, targets),
         target_ach = case_when(!(is.na(targets) | targets==0) ~ 
                                  cumulative/targets)) |> 
  arrange(desc(fiscal_year)) |> print()
  
 p_up |>  ggplot(aes(x=indicator)) +
  geom_col(aes(y=targets), fill=grey20k) +
  geom_col(aes(y=cumulative), width =0.5, fill=scooter) +
  geom_text(aes(y=top_col,
                label = scales::percent(target_ach, accuracy=1)),
            vjust=-0.75, size=5, color=grey80k) +
  facet_wrap(~fiscal_year, nrow = 1) +
  si_style_xyline() +
  # ylim(0,2300) +
  theme(plot.title = element_text(size = 18),
        axis.title = element_blank(),
        axis.text.x = element_text(angle = 90, hjust = 1, size=14),
        strip.text = element_text(face="bold", size=18, hjust=0.5)) +
  labs(title = str_glue("FY23Q2 {p_up$funding_agency} prevention cascade trehds for {p_up$pop}"),
       subtitle = "")

```

## check section 1a, 1b by fiscal year

TX_NEW ach for 1a, testing and prev for 1b

```{r}
p_up_trends <- usaid_pip |> filter(indicator %in% ind_prev) |>  
  filter(indicator %in% c("KP_PREV", "HTS_TST", "HTS_SELF")) |> 
  group_by(fiscal_year, indicator, funding_agency, pop) |> 
  summarise(across(targets:cumulative, ~sum(.x, na.rm = TRUE)), .groups = "drop") |> 
  mutate(indicator = fct_relevel(indicator, ind_prev),
         top_col = if_else(cumulative >= targets, cumulative, targets),
         target_ach = case_when(!(is.na(targets) | targets==0) ~ 
                                  cumulative/targets)) |> 
  arrange(desc(fiscal_year)) |> print()
  
 p_up_trends |>  ggplot(aes(x=fiscal_year, y=cumulative, color=indicator)) +
  geom_line() +
  geom_text(aes(label = cumulative),
            vjust=-0.75, size=5, color=grey80k) +
  si_style_xyline() +
  # ylim(0,2300) +
  theme(plot.title = element_text(size = 18),
        axis.title = element_blank(),
        axis.text.x = element_text(angle = 90, hjust = 1, size=14),
        strip.text = element_text(face="bold", size=18, hjust=0.5)) +
  labs(title = str_glue("FY23Q2 {p_up_trends$funding_agency} prevention cascade trehds for {p_up_trends$pop}"),
       subtitle = "")
```

## Check 1c by funding agency

```{r}
p_pp_trends <- pepfar_pip |> filter(indicator %in% ind_prev) |>  
  filter(indicator %in% c("PrEP_NEW")) |> 
  group_by(fiscal_year, indicator, funding_agency, pop) |> 
  summarise(across(targets:cumulative, ~sum(.x, na.rm = TRUE)), .groups = "drop") |> 
  mutate(indicator = fct_relevel(indicator, ind_prev),
         top_col = if_else(cumulative >= targets, cumulative, targets),
         target_ach = case_when(!(is.na(targets) | targets==0) ~ 
                                  cumulative/targets)) |> 
  arrange(desc(fiscal_year)) |> print()
  
 p_pp_trends |>  ggplot(aes(x=fiscal_year, y=cumulative, color=funding_agency)) +
  geom_line(aes(grou=funding_agency)) +
  geom_text(aes(label = cumulative),
            vjust=-0.75, size=5, color=grey80k) +
  si_style_xyline() +
  # ylim(0,2300) +
  theme(plot.title = element_text(size = 18),
        axis.title = element_blank(),
        axis.text.x = element_text(angle = 90, hjust = 1, size=14),
        strip.text = element_text(face="bold", size=18, hjust=0.5)) +
  labs(title = str_glue("FY23Q2 {p_pp_trends$funding_agency} prevention cascade trehds for {p_pp_trends$pop}"),
       subtitle = "")
 
 #off by 4, due to Jamaica CDC
 p_pp_trends <- pepfar_pip |> filter(indicator %in% ind_prev) |>  
  filter(indicator %in% c("PrEP_NEW"),
         funding_agency == "HHS/CDC",
         fiscal_year == 2023) |> 
  group_by(fiscal_year, country, indicator, funding_agency, pop) |> 
  summarise(across(targets:cumulative, ~sum(.x, na.rm = TRUE)), .groups = "drop") |> 
  mutate(indicator = fct_relevel(indicator, ind_prev),
         top_col = if_else(cumulative >= targets, cumulative, targets),
         target_ach = case_when(!(is.na(targets) | targets==0) ~ 
                                  cumulative/targets)) |> 
  arrange(desc(cumulative)) |> print()
  
 #Explore further
readRDS(file = rds) |>
  filter(fiscal_year ==2023,
         indicator %in% c("PrEP_NEW"),
         country == "Jamaica",
         disaggregate != "KeyPop/Status",
         otherdisaggregate_sub %in% c("People in prisons and other enclosed settings", "MSM"))

#There is likely a duplication somewhere as the dashboard shows double the values in the data for PrEP_NEW
```

There is likely a duplication somewhere as the dashboard shows double the values in the data for PrEP_NEW for both MSM and Prisoners in Jamaica for mech code 81219. **This was corrected as of 2 July 2023, based on code changes made June 30 to resolve a merge error 1:many on geographic units for some regional programs.**
