---
title: "snapshot_and_cascades"
author: "bourke betz"
format: html
    page-layout: full
    body-width: 900px
editor: visual
---

```{r}

```

Custom Lists

```{r}
pos <-  c("HTS_TST_POS", "TX_NEW", "TX_CURR", "TX_PVLS_D", "TX_PVLS_N")
neg <-  c("KP_PREV", "HTS_TST", "HTS_TST_NEG", "HTS_SELF", "PrEP_NEW", "PrEP_CT", "PrEP_CURR")
# mal_im <- c("81764","81759")

agency_order <- c("USAID", "CDC", "DOD", "HHS/HRSA", "Dedup")
keypop_order <- c("FSW", "MSM", "TG", "Prisoners", "PWID")
```

Custom colors

```{r}
keypop_colors <- c(FSW = "#005e7a", MSM = "#f28965", TG = "#7ecfc0", Prisoners = "#990d2e", PWID = "#fbcc50")

agency_colors <- c("USAID" = "#002f6c", "CDC" = "#a7c6ed", 
                               "DOD" = "#ba0c2f", "HHS/HRSA" = "#cfcdc9", 
                               "Dedup" = "#7ecfc0")
agency_colors_text <- c("USAID" = grey10k, "DOD" = grey10k, "CDC" = grey90k, "HHS/HRSA" = grey90k, "Dedup" = grey90k)
# agency_colors_text[is.na(match(agency_order, names(agency_colors_text)))] <-  "black"

```

### Global USAID Prevention Cascade

PEPFAR 2023-4 all correct.

```{r}
check |> count(funding_agency)
cascade <- check %>% filter(
                            # !country %in% c("Ukraine", "Tanzania", "Eswatini"),
                            # funding_agency == "CDC",
                            # mech_code %in% mal_im,
                            fy >= max(fy) - 2,
                            # fy < 2024,
                            disagg == "KP", 
                            indicator %in% neg) %>%
  group_by(fy, indicator, disagg) %>%
  summarise(sum.cum=sum(cumulative), sum.targ=sum(targets), .groups = "drop") |> print()

cascade %>% 
  ggplot2::ggplot(aes(x = indicator)) + 
    geom_col(aes(y = sum.cum)) + 
    geom_col(aes(y=sum.targ), fill = "gray", alpha = 0.4, width =0.5) +
    geom_text(color = "black", position = position_stack(vjust = 0.9), aes(y=sum.cum, label = sum.cum)) + 
geom_text(color = "black", position = position_stack(vjust = 0.9), aes(y=sum.targ, label = sum.targ)) + 

  facet_wrap(~ fy) + 
  theme(panel.background = element_blank(),
        legend.position = "none",
        axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs(title = glue::glue("PEPFAR {cascade$disagg} prevention cascade by FY"),
       y="cumulative")


```

### Global PEPFAR Treatment Cascade

PEPFAR 2024 all correct. USAID correct for prior years, small discrepancies for CDC Targets.

```{r}
#positive cascade
cascade <- check %>% filter(
                            disagg == "KP",
                            indicator %in% pos, 
                            # funding_agency=="USAID",
                            # str_detect(mech_name, "EpiC"),
                            fy >= max(fy) - 2,
                            ) %>%
  group_by(fy, indicator, disagg) %>%
  summarise(sum.cum=sum(cumulative), sum.targ=sum(targets), .groups = "drop") 

cascade %>%
  ggplot2::ggplot(aes(x = indicator)) + 
    geom_col(aes(y = sum.cum, fill = factor(fy))) + 
    geom_col(aes(y=sum.targ), fill = "gray", alpha = 0.4, width =0.5) +
    geom_text(color = "black", position = position_stack(vjust = 0.9), aes(y=sum.cum, label = sum.cum)) + 
  geom_text(color = "black", position = position_stack(vjust = 0.9), aes(y=sum.targ, label = sum.targ)) + 
  facet_wrap(~ fy) + 
  theme(panel.background = element_blank(),
        legend.position = "none",
        axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs(
  title = glue::glue("USAID {cascade$disagg} treatment cascade by FY"),
  y="cumulative")

```

### PEPFAR cascade comparison by agency

correct

```{r}

compare_pos_cascade <- check %>%
  filter(
  # country=="Ethiopia",                            
         indicator %in% pos, 
         fy == max(fy),
         # funding_agency!="Dedup",
         disagg == "KP",) %>%
  # mutate(funding_agency = reorder(funding_agency, 
                                  # match(funding_agency, agency_order))) |> 
  group_by(indicator, funding_agency, fy, ) %>%
  summarise(sum.cum = sum(cumulative),
            sum.targ = sum(targets),
            ach = sum(cumulative)/sum(targets),
            .groups = "drop") 

compare_pos_cascade %>% 
  ggplot(aes(x=indicator)) + 
  geom_col(aes(y=sum.cum, fill = funding_agency)) +
  geom_text(aes(y=sum.targ+2000, label=scales::percent(ach, 1)), color = "red") +
  geom_text(aes(y=0.9*(sum.cum), label=sum.cum, color = funding_agency)) +
  scale_fill_manual(values = agency_colors) +
  scale_color_manual(values = agency_colors_text) +
  facet_grid(cols=vars(funding_agency)) +
  theme(panel.background = element_blank(),
        legend.position = "none",
        axis.text.x = element_text(angle = 90, hjust = 1)) + 
    labs(title = glue::glue("PEPFAR treatment cascade by funding agency, {compare_pos_cascade$fy}"), y="cumulative")
```

clean

```{r}
compare_cascade_by_b <- check %>%
  filter(
    # country=="Nepal",                            
         indicator %in% neg, 
         fy == max(fy),
         # funding_agency=="USAID",
         # snu1 %in% c("Maputo","Sofala", "Tete", "Manica"),
         # snu1 %in% c("Central Province","Copperbelt Province", "Lusaka Province"),

         disagg == "KP",) %>%
  group_by(indicator, keypop, fy, 
           # country, 
           # funding_agency
           ) %>%
  summarise(sum.cum = sum(cumulative),
            sum.targ = sum(targets),
            ach = sum(cumulative)/sum(targets),
            .groups = "drop")
  
compare_cascade_by_b %>% ggplot(aes(x=indicator)) +
  geom_col(aes(y=sum.cum, fill = keypop)) +
  geom_text(aes(y=sum.targ+2000, label=scales::percent(ach, 1)), color = "red") +
  geom_text(aes(y=0.85*(sum.cum), label=sum.cum), color = "white") +
  facet_wrap(facets = vars(keypop), nrow=1) +
  scale_fill_manual(values=keypop_colors) +
  theme(panel.background = element_blank(),
        legend.position = "none",
        axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs(title = glue::glue("prevention cascade by key pop, {compare_cascade_by_b$fy}"),y="cumulative")
```

custom indicator cascades were checked against MER data manually, and custom indicators assessed for reasonability. One filter was revised as it needed to be updated to remove duplication.
