---
title: "read_msd"
author: "Bourke Betz"
format: html
editor: visual
---

Identify the name of the latest PSNU x IM MER Structured Data Set

```{r}

file <- glamr::return_latest(folderpath =  "../../Data/", pattern = "PSNU_IM_FY2")

# file2 <- glamr::return_latest(folderpath =  "../../Data/", pattern = "PSNU_IM_FY1") 


file_name <- str_extract(file, "(?<=Data\\/).+(?=\\.rds)") 
# file_name2 <- str_extract(file2, "(?<=Data\\/).+(?=\\.rds)") 
```

![](data:image/png;base64,iVBORw0KGgoAAAANSUhEUgAAACgAAAAaCAYAAADFTB7LAAAAa0lEQVR42u3OywnAIBBAwcXSUoCW5D11xDoNCBGNv0MOecJOBSOi1OZMsJ4dvFxEJ1OQnMxBarIKEpNNkJbsBknJYZCSnAYJyVVQziNig7/nZkFEbhTE5HpBVO4dxOXKIDL3BLG5BJ1T6rsbMfep2CaMN00AAAAASUVORK5CYII= "Run Current Chunk")

Read MSD

```{r}
mer_df <- gophr::read_psd(file)

# nepal_msd <- mer_df |> filter(country == "Nepal") |> glimpse()

# mer_df2 <- gophr::read_psd(file2, save_rds = TRUE, remove_txt = FALSE) %>% 
  # filter(fiscal_year>=2019)
```

Define indicator list and functions

```{r}
indicator_list <- c("KP_PREV",  "HTS_SELF", "HTS_TST", "HTS_TST_NEG", "PrEP_NEW", "PrEP_CT", "PrEP_CURR", "HTS_TST_POS",
                    "TX_NEW", "TX_CURR", "TX_PVLS", "TX_PVLS_D", "TX_PVLS_N", "TX_CURR_Lag1", "TX_CURR_Lag2", "TX_ML", "TX_NET_NEW")

kp_setup <- function(df) {
  df_ft <- df |> 
    # filter to relevant disaggs for standard KP analysis 
    filter(str_detect(standardizeddisaggregate, "KeyPop|Total|Sex|Preg"),
           indicator %in% indicator_list) |> 
    # Recode PVLS indicators to include NumDenom and Funding Agency = CDC
    mutate(indicator = 
           recode(indicator, "TX_PVLS" = paste0(indicator,"_",numeratordenom)),
                  funding_agency = recode(funding_agency, "HHS/CDC" = "CDC")) |> 
    # recode indicators as factor, rename fy, and create disagg variables for kp
    mutate(indicator = factor(indicator, levels = indicator_list),
           fy = fiscal_year,
         partner = prime_partner_name,
         disagg = str_extract(standardizeddisaggregate, "Total|KeyPop"),
         disagg = recode(disagg, "KeyPop" = "KP"),
         tx_ml_reason = case_when(indicator=="TX_ML" ~ 
                                    str_extract(otherdisaggregate, 
                                                "(?<=Outcome\\s-\\s).+")),
         keypop = str_extract(otherdisaggregate,
                              "FSW|MSM|TG|PWID|People\\sin\\sprisons"),
         keypop = recode(keypop, "People in prisons" = "Prisoners"),
         kp_prev_status = case_when(standardizeddisaggregate == "KeyPop/Status" ~ 
                                      str_extract(categoryoptioncomboname, 
                                                  "(?<=\\,\\s).+$"))
      ) |> 
    arrange(indicator)
  
  return(df_ft)
}

kp_clean <- function(df, time = NULL, focus = NULL) {
    #setup analytic prep for quarterly trend analysis
    if (!is.null(time)) {
    if (time == "fyq") {
      df2 <- df |> 
        filter(fiscal_year >= max(fiscal_year) - 1
               # create alternative for q2 or q3 when targets from COP shift this)
                 ) %>%
      # select fields relevant for quarterly analysis, excluding cumulative and targets
      select(operatingunit, country, contains("snu"), partner, mech_code, 
             mech_name, indicator, funding_agency, numeratordenom, 
             disagg, otherdisaggregate, sex, ageasentered, 
             standardizeddisaggregate, otherdisaggregate, keypop, 
             safe_for_net_new, safe_for_vlc,
             kp_prev_status, fy, qtr1, qtr2, qtr3, qtr4) |> 
      # recode indicator and arrange for viz PURPOSES
      mutate(indicator = factor(indicator, levels = indicator_list))|>  
      arrange(indicator) |> 
      # pivot to long format
      pivot_longer(qtr1:qtr4, names_to = "qtr", 
                   values_to = "results" ) |> 
      mutate(results = coalesce(results, 0),
         qtr = str_replace(qtr, "qtr","Q"),
         fyq = paste0("FY",str_extract(fy, "..$"), " ", qtr))
      
    #setup analytic prep for fiscal year achievement, trend, and target achievement analysis
    } else if (time == "fy") {
       df2 <- df |> 
         filter(standardizeddisaggregate != "KeyPop/Status") |> 
         mutate(
            cumulative = coalesce(cumulative, 0),
            targets = coalesce(targets, 0),
         ) |> 
         select(operatingunit, country, contains("snu"), partner, 
                mech_code, mech_name, indicator, funding_agency, 
                numeratordenom, disagg, standardizeddisaggregate, 
                safe_for_net_new, safe_for_vlc, sex, ageasentered,
                tx_ml_reason, keypop, fy, targets, cumulative) |> 
         mutate(indicator = factor(indicator, 
                                   levels = indicator_list)) |> 
         arrange(indicator)
    
    #print warning input if time is missing   
    }  else {
      stop("Invalid value for 'time'. Please specify 'quarterly' or 'annual'.")
    }
    
  } else if (!is.null(focus)) {    
      if (focus == "mmd") {
      df2 <- df |> 
        filter(str_detect(indicator,"TX_CURR(?!_Lag)"),
               str_detect(standardizeddisaggregate, "ARVDispense|Total")) |> 
        mutate(cumulative = coalesce(cumulative, 0),
        targets = coalesce(targets, 0),
        partner = prime_partner_name,
        fy = fiscal_year,
        arv = str_extract(otherdisaggregate, "(?<=-\\s).+")) |> 
  select(operatingunit, country, contains("snu"), partner, mech_code, mech_name, indicator, funding_agency, numeratordenom, standardizeddisaggregate, arv, otherdisaggregate, fy, targets, cumulative)
    } else if (focus == "modality") {
      df2 <- df |> 
        filter(str_detect(standardizeddisaggregate, "KeyPop|Total") == FALSE,
                          str_detect(indicator, "HTS_TST") == TRUE
               ) %>%
        pivot_longer(qtr1:qtr4, names_to = "qtr", values_to = "results" ) %>%
        mutate(results = coalesce(results, 0),
          qtr = str_replace(qtr, "qtr","Q"),
          fy = fiscal_year,
          fyq = paste0("FY",str_extract(fy, "..$"), " ", qtr),
          age = trendscoarse) %>%
      select(operatingunit, country, contains("snu"), prime_partner_name, mech_code, mech_name, indicator, funding_agency, numeratordenom,
             standardizeddisaggregate, modality, fy, fyq, results, age, ageasentered, sex)
    }  else {
      stop("Invalid value for 'focus'. Please set 'mmd' or 'modality' for focus")
    }
  } else {
    stop("At least one of 'time' and 'focus' must be specified.")

}
  
  return(df2)
}
# 
# # define function to run prep for KP adjacent analyses
# kp_adjacent <- function(df, focus) {
#   if (focus == "mmd"){
#     
#   } else if (focus = "modality") {
#     
#   } else {
#     stop("Invalid input for 'focus'. Please specify "mmd" or ")
#   }
#     
#   
#   return(df_focus)
# }

```

transform using the kp_setup() function and kp_time()

```{r}
check <- mer_df %>% kp_setup() |> kp_clean(time = "fy")
qcheck <- mer_df %>% kp_setup() |> kp_clean(time = "fyq")

mmd <- mer_df |> kp_setup() |> kp_clean(focus = "mmd")
modality <- mer_df |> kp_setup() |> kp_clean(focus = "modality")
```

```{r}
rm(mer_df)
gc()
# rm(mer_df2)

```
