---
title: "PrEP uptake by population"
author: "Bourke Betz"
format: html
editor: visual
---

Identify the name of the latest PSNU x IM MER Structured Data Set

```{r}
theme_clean_axis_legends <-  theme(axis.title = element_blank(),
        legend.position = "none",
        legend.title = element_blank())

```

```{r}

ayp <- c("15-19", "20-24", "25-29")
ind <- c("PrEP_NEW", "PrEP_CT")

prep_trends_pre <- qcheck |> 
  filter(indicator %in% c("PrEP_NEW", "PrEP_CT"),
         funding_agency == "USAID",
         !(country=="Uganda" & !is.na(keypop))) |> 
  mutate(pop = case_when(
    !is.na(keypop) ~ keypop,
    disagg == "PregnantOrBreastfeeding" ~ otherdisaggregate,
    sex == "Female" & ageasentered %in% ayp ~ "AGYW",
    sex == "Male" & ageasentered %in% ayp ~ "ABYM",
    standardizeddisaggregate == "Total Numerator" ~ "Total"
    )) |> 
  filter(
    # !is.na(pop),
    fy != 2024,
    fyq != "FY23 Q4"
         ) |> 
  group_by(indicator, pop, fy, qtr, fyq) |> 
  summarise(results=sum(results), .groups = "drop")

prep_pop_trends <- prep_trends_pre |> filter(pop!="Total")
  
prep_trends <- prep_trends_pre |> filter(pop=="Total") |>  rename(total = results) |> select(-pop) |> 
  right_join(prep_pop_trends, multiple = "all", ) |> 
  mutate(pop = fct_relevel(pop,
    "AGYW", "FSW", "MSM", "ABYM"),
    population = recode(pop,
                        "AGYW" = "Adolescent girls & young women (15-29)",
                        "FSW"  = "Female sex workers",
                        "MSM"  = "Men who have sex with men",
                        "ABYM" = "Adolescent boys & young men (15-29)",
                        "TG" = "Transgender",
                        "PWID" = "People who inject drugs"
                        ),
  indicator1 = "PrEP initiations",
  indicator2 = "PrEP continuations") |>
  #label value for max and series start/end
  group_by(pop, indicator) |> 
  mutate(percent_of_total_series_ends = case_when(
          fy == min(fy) & qtr == "Q1" ~ scales::percent(results/total, accuracy = 1),
          fy == max(fy) & qtr == "Q3" ~ scales::percent(results/total, accuracy = 1),
          # results/total == max(results/total) ~ scales::percent(results/total, accuracy = 1),
          )) |> 
  ungroup() |> arrange(indicator, pop, fyq)

rm(prep_trends_pre, prep_pop_trends)


```

### PrEP_NEW trends - by large priority pop
```{r, fig.retina=2}
akp <- c("#33adbb", "#005e7a", "#f28965", "#b85534")
agyw_last2_color <- c(grey60k, "#33adbb", grey30k)

prep_trends_smallx <- prep_trends |> filter(indicator == ind[1],
                          !pop %in% c("Pregnant", "Breastfeeding", "TG", "PWID", "Prisoners")) |> 
  mutate(agyw_last2 = case_when(pop=="AGYW" & fyq %in% c("FY23 Q2", "FY23 Q3") ~ "focus",
                                pop!="AGYW" & fyq %in% c("FY23 Q2", "FY23 Q3") ~ "attention",
                                .default = "norm")) |> group_by(pop, agyw_last2) |> 
  ggplot(aes(x=fyq)) +
  # geom_bar(aes(y=total), alpha = 0.4, fill = "grey", stat = "summary", fun = "mean") +
  geom_bar(aes(y=results, fill = agyw_last2), stat = "identity",  position = "dodge2") +
  facet_wrap(~population, nrow = 1, labeller = label_wrap_gen(width = 20)) +
  geom_text(aes(y=results+5000, label=percent_of_total_series_ends,  color = agyw_last2), position = position_dodge2(width = 1), fontface="bold", size=4) +
  # geom_text(aes(y=results+20000, color = pop, label=percent_of_total,   position = position_dodge2(width = 1)) +
  scale_fill_manual(values=agyw_last2_color) +
  scale_color_manual(values=agyw_last2_color) +
  scale_y_continuous(labels = comma, breaks = c(25000, 50000, 75000, 100000, 125000, 150000),  limits = c(0, 160000), expand = c(0, 0)) +
  # scale_color_discrete(akp) +
  si_style_ygrid() +
  theme(
      #format axes
        axis.title = element_blank(),
        axis.text.x.bottom = element_text(angle=90, vjust = 0.3),
        # panel.grid.minor.y = element_line(color = grey10k),
        panel.grid.major.y = element_line(color = grey10k),
      #format facet titles
        strip.text.x.top = element_text(hjust = 0.5, vjust = 0, face = "bold", size = 16),
      #format legends
        legend.position = "none",
        legend.title = element_blank(),
      #format plot title
        plot.title = element_markdown(face="bold", size = 36),
        plot.subtitle = element_markdown(size=14),
        plot.caption = element_markdown(size=11, margin = margin(t=20))

      ) +
  labs(
    # title  = HTML(str_glue("PrEP initiations continue to increase, <span style='color: #33adbb;'>especially for AGYW")),
    subtitle  = "USAID global PrEP_NEW trends and percent of total by population",
    caption = str_glue("Data source: {file_name},  \nexcluding Uganda where KP disaggregate reporting was paused  \nNote: Populations may overlap (e.g. a 23yo FSW would also be in AGYW but a 34yo MSM would not be in ABYM)"),
    color = "Population") 

prep_trends_smallx

ggsave(plot=prep_trends_smallx, filename = paste0("../../Images/OHA Q3/prep_trends_smallx.png"), width = 11.5, height = 7)
```

#### PrEP_NEW trends - small priority populations
```{r}
last2_color <- c(grey60k, grey30k)

prep_trends_smallerx <- prep_trends |> filter(indicator == ind[1],
                          pop %in% c("TG", "PWID")) |> 
    mutate(last2 = case_when(pop!="AGYW" & fyq %in% c("FY23 Q2", "FY23 Q3") ~ "attention",
                                .default = "norm")) |> 
  ggplot(aes(x=fyq)) +
  geom_bar(aes(y=results, fill=last2), stat = "identity",  position = "dodge2") +
  scale_fill_manual(values=last2_color) +
  facet_wrap(~pop, nrow = 1, labeller = label_wrap_gen(width = 20)) +
    scale_y_continuous(labels = comma, 
                     n.breaks = 3,
                     minor_breaks = waiver(), 
                     limits = c(0, 5200), 
                     expand = c(0, 0)) +
  si_style_ygrid() +
  theme(
      #format axes
        axis.title = element_blank(),
        axis.text.x.bottom = element_blank(),
        axis.text.y = element_text(size=6),
          # element_text(angle=90, vjust = 0.3),
        panel.grid.minor.y = element_blank(),
        panel.grid.major.y = element_line(color = grey10k),
      #format facet titles
        strip.text.x.top = element_text(hjust = 0.5, vjust = 0, face = "bold", size = 7),
      #format legends
        legend.position = "none",
        legend.title = element_blank(),
      #format plot title
        plot.title = element_markdown(face="bold", size = 36),
        plot.subtitle = element_markdown(size=14),
        plot.caption = element_markdown(size=11, margin = margin(t=20))) 

prep_trends_smallerx

ggsave(plot=prep_trends_smallerx, filename = paste0("../../Images/OHA Q3/prep_trends_smaller_pops.png"), width = 2, height = 1.5)
```

### PrEP_NEW trends - total
```{r}
vert_adjust <- c(30000)

prep_trends_total <- prep_trends |> filter(indicator == ind[1],
                          !pop %in% c("Pregnant", "Breastfeeding")) |> 
  ggplot(aes(x=fyq, group = indicator)) +
  geom_line(aes(y=total), color = grey10k, stat = "summary", fun = "mean", size=1.5) +
  # geom_bar(aes(y=total), alpha = 0.4, color = "grey", stat = "summary", fun = "mean") +
  geom_text(aes(y=total+vert_adjust, label=comma(
    case_when(qtr %in% c("Q1", "Q3")  ~ total)
  )), stat = "summary", fun ="mean", size=4) +
  geom_text(aes(y=total-vert_adjust, label=
                      case_when(qtr %in% c("Q1", "Q3")  ~ fyq)),
            color = grey40k, size=4) +
  si_style_nolines() +
  scale_y_continuous(labels = comma, 
                     n.breaks = round(max(prep_trends$total)/150000),
                     # breaks = c(50000, 150000, 250000), minor_breaks = waiver(), 
                     limits = c(min(prep_trends$total)-vert_adjust, max(prep_trends$total)+vert_adjust)
                     ) +
  theme_clean_axis_legends +
    theme(
      axis.text = element_blank(),
      # panel.grid.major.y = element_line(color = grey10k),
        plot.subtitle = element_markdown(size=14),
        plot.caption = element_markdown(size=11, margin = margin(t=0))
      ) +
  labs(
    subtitle  = "USAID Global PrEP_NEW total result trends",
    caption = str_glue("Data source: {file_name}"),

  )

prep_trends_total

ggsave(plot=prep_trends_total, filename = paste0("../../Images/OHA Q3/prep_trends_total.png"), width = 16, height = 2.5)


```




### Prep_CT trends by large priority pop

```{r, fig.retina=2}

fsw_last2_color <- c(grey60k, "#005e7a", grey30k)


prep_ct_trends_smallx <- prep_trends |> filter(indicator == ind[2],
                          !pop %in% c("Pregnant", "Breastfeeding", "TG", "PWID", "Prisoners")) |> 
  mutate(agyw_last2 = case_when(pop=="FSW" & fyq %in% c("FY23 Q2", "FY23 Q3") ~ "focus",
                                pop!="FSW" & fyq %in% c("FY23 Q2", "FY23 Q3") ~ "attention",
                                .default = "norm")) |> 
  ggplot(aes(x=fyq)) +
  geom_bar(aes(y=results, fill = agyw_last2), stat = "identity",  position = "dodge2") +
  facet_wrap(~population, nrow = 1, labeller = label_wrap_gen(width=20)) +
  geom_text(aes(y=results+5000, label=percent_of_total_series_ends,  color = agyw_last2), position = position_dodge2(width = 1), fontface="bold", size=4) +
  # geom_text(aes(y=results+20000, color = pop, label=percent_of_total,   position = position_dodge2(width = 1)) +
  scale_fill_manual(values=fsw_last2_color) +
  scale_color_manual(values=fsw_last2_color) +
  scale_y_continuous(labels = comma, breaks = c(25000, 50000, 75000, 100000, 125000), limits = c(0, 160000), expand = c(0, 0)) +
  # scale_color_discrete(akp) +
  si_style_ygrid() +
  theme(
      #format axes
        axis.title = element_blank(),
        axis.text.x.bottom = element_text(angle=90, vjust = 0.3),
        panel.grid.minor.y = element_blank(),
        panel.grid.major.y = element_line(color = grey10k),
      #format facet titles
        strip.text.x.top = element_text(hjust = 0.5, vjust=0, face = "bold", size = 16),
      #format legends
        legend.position = "none",
        legend.title = element_blank(),
      #format plot title
        plot.title = element_markdown(face="bold", size = 36),
        plot.subtitle = element_markdown(size=14),
        plot.caption = element_markdown(size=11, margin = margin(t=20))

      ) +
    labs(
    # title  = HTML(str_glue("PrEP initiations continue to increase, <span style='color: #33adbb;'>especially for AGYW")),
    subtitle  = "USAID global PrEP_CT trends and percent of total by population",
    caption = str_glue("Data source: {file_name},  \nexcluding Uganda where KP disaggregate reporting was paused  \nNote: Populations may overlap (e.g. a 23yo FSW would also be in AGYW but a 34yo MSM would not be in ABYM)"),
    color = "Population") 


prep_ct_trends_smallx

ggsave(plot=prep_ct_trends_smallx, filename = paste0("../../Images/OHA Q3/pre_ct_trends_smallx.png"), width = 11.5, height = 7)
```


#### PrEP_NEW trends - small priority populations
```{r}
prep_ct_trends_smallerx <- prep_trends |> filter(indicator == ind[2],
                          pop %in% c("TG", "PWID", "Prisoners", "Pregnant", "Breastfeeding")) |> 
  mutate(pop = fct_relevel(pop, "Pregnant", "Breastfeeding", "TG", "PWID", "Prisoners")) |> 
  ggplot(aes(x=fyq)) +
  geom_bar(aes(y=results), stat = "identity",  position = "dodge2") +
  facet_wrap(~pop, nrow = 1, labeller = label_wrap_gen(width = 20)) +
    scale_y_continuous(labels = comma, 
                     n.breaks = 5,
                     minor_breaks = waiver(), limits = c(0, 3400), 
                     expand = c(0, 0)) +
  si_style_ygrid() +
  theme(
      #format axes
        axis.title = element_blank(),
        axis.text.x.bottom = element_text(angle=90, vjust = 0.3),
        panel.grid.minor.y = element_line(color = grey10k),
        panel.grid.major.y = element_line(color = grey10k),
      #format facet titles
        strip.text.x.top = element_text(hjust = 0.5, vjust = 0, face = "bold", size = 16),
      #format legends
        legend.position = "none",
        legend.title = element_blank(),
      #format plot title
        plot.title = element_markdown(face="bold", size = 36),
        plot.subtitle = element_markdown(size=14),
        plot.caption = element_markdown(size=11, margin = margin(t=20))) +
  labs(
    subtitle  = "USAID Global PrEP_CT result trends and percent of total by population, excluding KP results for Uganda where KP disaggregate reporting is paused",
    ) 

prep_ct_trends_smallerx

ggsave(plot=prep_ct_trends_smallerx, filename = paste0("../../Images/OHA Q3/prep_ct_trends_smallerx.png"), width = 16, height = 5)
```

### PrEP_CT trends - total
```{r}
prep_ct_trends_total <- prep_trends |> filter(indicator == ind[2],
                          !pop %in% c("Pregnant", "Breastfeeding")) |> 
  ggplot(aes(x=fyq, group = indicator)) +
  geom_line(aes(y=total), color = grey10k, stat = "summary", fun = "mean", size=1.5) +
  # geom_bar(aes(y=total), alpha = 0.4, color = "grey", stat = "summary", fun = "mean") +
  geom_text(aes(y=total+vert_adjust, label=comma(
    case_when(qtr %in% c("Q1", "Q3")  ~ total)
  )), stat = "summary", fun ="mean", size=4) +
  geom_text(aes(y=total-vert_adjust, label=
                      case_when(qtr %in% c("Q1", "Q3")  ~ fyq)),
            color = grey40k, size=4) +
  si_style_nolines() +
  scale_y_continuous(labels = comma, 
                     n.breaks = round(max(prep_trends$total)/150000),
                     # breaks = c(50000, 150000, 250000), minor_breaks = waiver(), 
                     limits = c(min(prep_trends$total)-vert_adjust, max(prep_trends$total)+vert_adjust)
                     ) +
  theme_clean_axis_legends +
    theme(
      axis.text = element_blank(),
      # panel.grid.major.y = element_line(color = grey10k),
        plot.subtitle = element_markdown(size=14),
        plot.caption = element_markdown(size=11, margin = margin(t=0))
      ) +
  labs(
    subtitle  = "USAID Global PrEP_CT total result trends",
    caption = str_glue("Data source: {file_name}"),

  )

prep_ct_trends_total

ggsave(plot=prep_ct_trends_total, filename = paste0("../../Images/OHA Q3/prep_ct_trends_total.png"), width = 16, height = 2.5)
```

#### PrEP_CT PBF
which countries are reporting?
```{r}

prep_ct_trends_pbf <- prep_trends |> filter(indicator == ind[2],
                          pop %in% c("Pregnant", "Breastfeeding")) |> 
  mutate(pop = fct_relevel(pop, "Pregnant", "Breastfeeding")) |> 
  ggplot(aes(x=fyq)) +
  # geom_bar(aes(y=total), alpha = 0.4, fill = "grey", stat = "summary", fun = "mean") +
  geom_bar(aes(y=results, 
               # fill = pop
               ), stat = "identity",  position = "dodge2") +
  facet_wrap(~population, nrow = 1) +
  # geom_text(aes(y=results+20000, color = pop, label=percent_of_total,   position = position_dodge2(width = 1)) +
  # scale_fill_manual(values=akp) +
  # scale_color_manual(values=akp) +
  scale_y_continuous(labels = comma, 
                     n.breaks = 5,
                     minor_breaks = waiver(), limits = c(0, 7000), 
                     expand = c(0, 0)) +
  # scale_color_discrete(akp) +
  si_style_ygrid() +
  theme(
      #format axes
        axis.title = element_blank(),
        axis.text.x.bottom = element_text(angle=90, vjust = 0.3),
        panel.grid.minor.y = element_line(color = grey10k),
        panel.grid.major.y = element_line(color = grey10k),
      #format facet titles
        strip.text.x.top = element_text(hjust = 0.5, face = "bold", size = 16),
      #format legends
        legend.position = "none",
        legend.title = element_blank(),
      #format plot title
        plot.title = element_markdown(face="bold", size = 36),
        plot.subtitle = element_markdown(size=14),
        plot.caption = element_markdown(size=11, margin = margin(t=20))

      ) +
  labs(title  = HTML(str_glue("PrEP continuations continue to increase, <span style='color: #005e7a;'>especially for FSW")),
    subtitle  = "PrEP_CT result trends and percent of total by population",
    color = "Population") 

prep_ct_trends_pbf

ggsave(plot=prep_ct_trends_pbf, filename = paste0("../../Images/OHA Q3/prep_ct_trends_pbf.png"), width = 8, height = 6.5)
```


### PrEP_NEW  to PrEP_CT
USAID tends to initiate more AYP on PrEP than continuations, the inverse of CDC, which does less volume but more continuations
among KP there is more continuation than initiation across agencies
```{r}
prep_trends_fsw <- qcheck |> 
  filter(indicator %in% c("PrEP_NEW", "PrEP_CT")) |> 
  mutate(pop = case_when(
    keypop %in% c("MSM", "FSW") ~ keypop,
    disagg == "PregnantOrBreastfeeding" ~ otherdisaggregate,
    sex == "Female" & ageasentered %in% ayp ~ "AGYW",
    sex == "Male" & ageasentered %in% ayp ~ "ABYM",
    standardizeddisaggregate == "Total Numerator" ~ "Total"
    )) |> 
  filter(
         funding_agency %in% c("USAID", "CDC"),
    fy == 2023,
    !qtr %in% c("Q1", "Q4")) |> 
  group_by(funding_agency, indicator, pop, qtr, fyq) |> 
  summarise(results=sum(results), .groups = "drop") |> 
  pivot_wider(names_from = indicator, values_from = results) |> 
  mutate(ratio = PrEP_NEW/PrEP_CT) |> 
  select(-qtr) |> 
  arrange(pop, fyq, desc(funding_agency)) |> 
  print()

```

#### FSW PrEP declines exploration
```{r}
prep_trends_fsw <- qcheck |> 
  filter(indicator %in% c("PrEP_NEW", "PrEP_CT"),
         keypop == "FSW",
         funding_agency == "USAID") |> 
  mutate(pop = case_when(
    keypop %in% c("MSM", "FSW") ~ keypop,
    disagg == "PregnantOrBreastfeeding" ~ otherdisaggregate,
    sex == "Female" & ageasentered %in% ayp ~ "AGYW",
    sex == "Male" & ageasentered %in% ayp ~ "ABYM",
    standardizeddisaggregate == "Total Numerator" ~ "Total"
    )) |> 
  filter(
    !is.na(pop),
    fy == 2023,
    !qtr %in% c("Q1", "Q4")
         ) |> 
  group_by(country, indicator, pop, qtr) |> 
  summarise(results=sum(results), .groups = "drop") |> 
  pivot_wider(names_from = qtr, values_from = results) |> 
  clean_names() |> 
  mutate(drop = q2 > q3)

prep_trends_fsw |> filter(country == "Uganda")
```


##### PrEP_NEW trends - by large priority pop (bars in bar)
```{r}
akp <- c("#33adbb", "#005e7a", "#f28965", "#b85534")

prep_trends_barinbar <- prep_trends |> filter(indicator == ind[1],
                                                  !is.na(pop),
                          !pop %in% c("Pregnant", "Breastfeeding", "TG", "PWID", "Prisoners")) |> 
  ggplot(aes(x=fyq)) +
  geom_bar(aes(y=total), alpha = 0.4, fill = "grey", stat = "summary", fun = "mean") +
  geom_bar(aes(y=results, fill = pop), stat = "identity",  position = "dodge2") +
  geom_text(aes(y=results+20000, color = pop, label=scales::percent(results/total, 1)),   position = position_dodge2(width = 1)) +
  scale_fill_discrete(akp) +
  # scale_color_discrete(akp) +
  si_style_yline() +
  theme_clean_axis_legends +
  labs(title  = HTML(str_glue("{prep_trends$indicator1}  continue to increase, especially for AGYW (females 15-29)")),
    subtitle  = "PrEP_NEW totals and selected populations trends",
    color = "Population") 

# prep_trends_barinbar
```



#### PrEP expansion, country case-studies or 1+8+1
Zambia from Sarah
```{r}

```

### PrEP increases by country - success stories
```{r}
prep_trends_pop <- qcheck |> 
  filter(indicator %in% c("PrEP_NEW", "PrEP_CT"),
         funding_agency == "USAID",
         !(country=="Uganda" & !is.na(keypop))) |> 
  mutate(pop = case_when(
    keypop %in% c("MSM", "FSW") ~ keypop,
    disagg == "PregnantOrBreastfeeding" ~ otherdisaggregate,
    sex == "Female" & ageasentered %in% ayp ~ "AGYW",
    sex == "Male" & ageasentered %in% ayp ~ "ABYM",
    standardizeddisaggregate == "Total Numerator" ~ "Total"
    )) |> 
  filter(
    !is.na(pop),
    !(fy == 2022 & qtr %in% c("Q3", "Q2", "Q1")) &
    !(fy == 2023 & qtr == "Q4") & fy != 2024
         ) |> 
  group_by(country, indicator, pop, fyq) |> 
  summarise(results=sum(results, na.rm = TRUE), .groups = "drop") |> 
  mutate(indicator = str_to_lower(indicator)) 

write_csv(prep_trends_pop, "../../Dataout/OHA Q3/prep_trends.csv")

prep_trends_combos <- prep_trends_pop |>
  pivot_wider(names_from = c(indicator, fyq), values_from = results) |> 
  clean_names() |> 
  relocate(prep_ct_fy22_q4, .before = prep_ct_fy23_q1) |> 
  # filter(
  #   (prep_new_fy23_q3 >= 2*prep_new_fy23_q1 |
  #   prep_new_fy23_q3 >= 2*prep_new_fy22_q4) & prep_new_fy23_q3 >= 0.9* prep_new_fy23_q2
  #   | (prep_ct_fy23_q3 >= 2*prep_ct_fy23_q1 |
  #   prep_ct_fy23_q3 >= 2*prep_ct_fy22_q4) & prep_ct_fy23_q3 >= 0.9* prep_ct_fy23_q2
  #   ) |> 
  print()

prep_pop_combos <- prep_trends_combos |> select(country, pop) |> print()


prep_trends_meriting_exploration <- prep_trends_pop |> semi_join(prep_pop_combos)

prep_trends_meriting_exploration
```

Mozambique and Lesotho are the only possible stories for the USAID PBF numbers. We would need a compelling narrative
```{r}
prep_trends_pbf <- qcheck |> 
  filter(indicator %in% c("PrEP_NEW", "PrEP_CT"),
         funding_agency == "USAID",
         disagg == "PregnantOrBreastfeeding",
         !(country=="Uganda" & !is.na(keypop))) |> 
  mutate(pop = case_when(
    keypop %in% c("MSM", "FSW") ~ keypop,
    disagg == "PregnantOrBreastfeeding" ~ otherdisaggregate,
    sex == "Female" & ageasentered %in% ayp ~ "AGYW",
    sex == "Male" & ageasentered %in% ayp ~ "ABYM",
    standardizeddisaggregate == "Total Numerator" ~ "Total"
    )) |> 
  filter(
    !is.na(pop),
    !(fy == 2022 & qtr %in% c("Q3", "Q2", "Q1")) &
    !(fy == 2023 & qtr == "Q4") & fy != 2024
         ) |> 
  group_by(country, indicator, pop, fyq) |> 
  summarise(results=sum(results), .groups = "drop") |> 
  mutate(indicator = str_to_lower(indicator)) |>
  pivot_wider(names_from = c(indicator, fyq), values_from = results) |> 
  clean_names() |> 
  relocate(prep_ct_fy22_q4, .before = prep_ct_fy23_q1) |> 
  # filter(
  #   (prep_new_fy23_q3 >= 2*prep_new_fy23_q1 |
  #   prep_new_fy23_q3 >= 2*prep_new_fy22_q4) & prep_new_fy23_q3 >= 0.9* prep_new_fy23_q2
  #   | (prep_ct_fy23_q3 >= 2*prep_ct_fy23_q1 |
  #   prep_ct_fy23_q3 >= 2*prep_ct_fy22_q4) & prep_ct_fy23_q3 >= 0.9* prep_ct_fy23_q2
  #   ) |> 
  print()
```

